Crossing Origins by Crossing Formats

### 2012-11-22 main.tex
Section Crossing-origins complete.

\begin{abstract}
 In a heterogeneous system like the web, information is
exchanged between components in versatile formats. A new breed of attacks is on
the rise that exploit the mismatch between the expected and provided content.
\emph{Injection attacks} are becoming increasingly more sophisticated by
operating across multiple languages. \emph{Content repurposing} attacks supply
malicious payload that appears formatted as benign content. 
% 
This paper focuses on the root cause of a large class of attacks: \emph{polyglots}. 
A polyglot is aprogram that is valid in multiple programming languages. Polyglots allow
multiple interpretation of the content, providing a new space of attack vectors.
We characterize of what constitutes a dangerous format in the web setting and
identify particularly dangerous formats, with PDF as the prime example. We
demonstrate that polyglot-based attacks on the web open up for insecure
communication across Internet origins. We perform a systematic study of
PDF-based injection and content repurposing attacks. We evaluate the current
practice in client/server content filtering and PDF readers for polyglot-based
attacks, and report on vulnerabilities in the top 100 Alexa web sites. Our
recommendations for protective measures on server side, in browsers, and in content
interpreters (such as PDF readers) show how to mitigate the attacks.
\end{abstract}

@@

A malicious polyglot is composed of two formats where one is benign in nature and the other
contains a malicious payload. 
% Under what circumstances can a polyglot be malicious
This kind of polyglot can be used for malicious purposes when there is a difference between
the expected run-time context and the actual context it is executed in. 
In the expected context the content would be interpreted as the 
benign format. In the actual context, however, the content is coerced to be 
interpreted as the malicious format containing the payload.

@@

In a web context, 
% Characteristics of a malicious polyglot

@@

% We have identified two classes of malicious polyglots; those based on syntax injection, and those based on content repurposing.

If the content is verified to be benign in

  In the situation where

at the time of verification compared to time of use

It is possible to create such a polyglot by mixing content, that is benign when
verified, with content, that is malicious when executed. The verification
process will see the benign content and allow it

In literature we find Content repurposing, content smuggling, chameleon, gifar

@@

% Description of attack technique 
A content repurposing attack attacks a website
that allows and serves user supplied files. This could be a file sharing
service, an image database, or a job search service. The files are verified to
be of a certain benign file type, e.g. an image, before being served to the end
user. By submitting a polyglot to such a service, an attacker can trick the
service into serving malicious content under the origin of the service. The
service will verify the file, assuming that it is of the benign format, but once
the content is served an attacker can coerce the content to be interpreted as
the malicious format.

>>>>

\begin{abstract}
 In a heterogeneous system like the web, information is
exchanged between components in versatile formats. A new breed of attacks is on
the rise that exploit the mismatch between the expected and provided content.
\emph{Injection attacks} are becoming increasingly more sophisticated by
operating across multiple languages. \emph{Content repurposing} attacks supply
malicious payload that appears formatted as benign content. 
% 
This paper focuses on the root cause of a large class of attacks: \emph{polyglots}. 
A polyglot is a program that is valid in multiple programming languages. Polyglots allow
multiple interpretation of the content, providing a new space of attack vectors.
We characterize of what constitutes a dangerous format in the web setting and
identify particularly dangerous formats, with PDF as the prime example. We
demonstrate that polyglot-based attacks on the web open up for insecure
communication across Internet origins. We perform a systematic study of
PDF-based injection and content repurposing attacks. We evaluate the current
practice in client/server content filtering and PDF readers for polyglot-based
attacks, and report on vulnerabilities in the top 100 Alexa web sites. Our
recommendations for protective measures on server side, in browsers, and in content
interpreters (such as PDF readers) show how to mitigate the attacks.
\end{abstract}

@@

A malicious polyglot is composed of two formats where one is benign in nature and the other
contains a malicious payload. 
% Characteristics of a malicious polyglot
The benign format would preferably be a widely accepted format with the capability 
of hiding arbitrary data, e.g. an image with comment fields. The malicious file 
format would ideally have strong capabilities, s
% Under what circumstances can a polyglot be malicious
This kind of polyglot can be used for malicious purposes when there is a difference between
the expected run-time context and the actual context it is executed in. 
In the expected context the content would be interpreted as the 
benign format. In the actual context, however, the content is coerced to be 
interpreted as the malicious format containing the payload.

@@

In a web context, coercing content to be interpreted as a different type be 
done easily. If the content is loaded using an image-tag it will be interpreted 
as an image, if a script-tag is used it will be interpreted as a script. Some 
tags even let the developer decide which type to interpret the content as. 
To prevent abuse, the browsers employ content-type 
sniffing for certain content-types, a practice which has historically led to 
security issues.

@@

We have identified two vectors in which malicious polyglots can be used for 
exploitation; syntax injection, and content repurposing.

%It is possible to create such a polyglot by mixing content, that is benign when
%verified, with content, that is malicious when executed. The verification
%process will see the benign content and allow it

%In literature we find Content repurposing, content smuggling, chameleon, gifar

@@

% Description of attack technique 
A content repurposing attack targets the users of a website
that allows and serves user supplied files. This could be a file sharing
service, an image database, or a job search service. The service would only 
accept a limited set of file-types, and the files are verified to
be of one of these types, e.g. an image, before being served to the end
user. By submitting a polyglot to such a service, an attacker can trick the
service into serving malicious content under the origin of the service. The
service will verify the file, assuming that it is of the benign format, but once
the content is served an attacker can coerce the content to be interpreted as
the malicious format.
